---
title: "GeospatialMapping"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

### Visualizing Geospatial Data

Using the leaflet library we can quickly load in some geo-spatial data, then visualize it on a map very easily.

```{r, echo=FALSE}
library(leaflet)
leaflet(quakes) %>% addTiles() %>% addMarkers(
  clusterOptions = markerClusterOptions()
)
```

### Popups and Markers

You can quickly create markers for various places.

```{r, echo=FALSE}
content <- paste(sep = "<br/>",
  "<b><a href=''>UT Dallas</a></b>",
  "800 W Campbell Road",
  "Richardson, TX 75040"
)

leaflet() %>% addTiles() %>%
  addPopups(-96.748254, 32.985636, content,
    options = popupOptions(closeButton = FALSE)
  )
```

### Learning on Geospatial Data

So I eventually want to come back to this data, in order to do some cool machine learning on it but as of right now I am really lazy and just wanted to look at leaflet becuase it looks so cool, but later on I will be implementing learning on geospatial data.